\documentclass{bredelebeamer}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{makecell}
%\usepackage{media9} % for movies
%\usepackage{multimedia} % for movies
\usepackage{caption} % for figure caption
\usepackage{animate}
\usepackage[final]{listings} % for listing source code
\usefonttheme[onlymath]{serif} % make the equations look better
% define box for listing
\definecolor{myblue}{HTML}{4C72B0}
\definecolor{myred}{HTML}{C54E52}
\definecolor{mygreen}{HTML}{56A968}
\lstset{
      language=C++,
      basicstyle=\ttfamily,
      frame=single,
      columns=flexible,
      breaklines=true,
      commentstyle=\color{mygreen},
      keywordstyle = \color{myblue},
      stringstyle  = \color{orange},
      }
\usepackage[absolute,overlay]{textpos} 
\setlength{\parskip}{0.9em}
\setbeamertemplate{navigation symbols}{}
\newcommand*\dif{\mathop{}\!\mathrm{d}}
%%%%%%%%% some settings
\captionsetup[figure]{labelformat=empty} % remove the prefix 'figure' for figure caption
\captionsetup[table]{labelformat=empty} % remove the prefix 'table' for figure caption
\setbeamertemplate{headline}{} %%%%%%%%%%% remove header %%%%%%%%%%%
\setbeamerfont{frametitle}{size=\Large} %% title font size
\renewcommand{\arraystretch}{1.5} % line space in a table
%%%%%%%%%% title
\title[ ]{DAFoam Workshop 2024}
\subtitle{v3.1.2}

\author{Ping He\\ ~ \\July 25, 2024 }


\date[July 25, 2024]{}

\setbeamercolor{title}{fg=Black,bg=White!0}
\setbeamercolor{frametitle}{fg=Black,bg=White!0}
%gets rid of footer
%will override 'frame number' instruction above
%comment out to revert to previous/default definitions
\setbeamertemplate{footline}[page number]

\begin{document}

%---------------------------------------------------------------%
\begin{frame}
  \titlepage
\end{frame}

%---------------------------------------------------------------%


%---------------------------------------------------------------%
\begin{frame}{Objectives}

In this workshop, we will
\begin{itemize}
  \setlength\itemsep{1em}
 \item Introduce DAFoam's new features.
 \item Have DAFoam users present their latest research.
 \item Discuss how to promote a more interactive community.
\end{itemize}

\end{frame}
%---------------------------------------------------------------%

%---------------------------------------------------------------%
\begin{frame}{Schedule (Morning)}
\small
\begin{tabularx}{\textwidth}{lX}
 09$:$00--09$:$30 & Ping He, Iowa State University. ``Introduction to DAFoam's latest features" \\ 
 09$:$30--10$:$00 & Chengyu Wu, Tsinghua University. ``More generalizable data driven turbulence models based on FIML using DAFoam" \\  
 10$:$00--10$:$30 & Bernardo Pacini, University of Michigan. ``Multidisciplinary design optimization of propeller-driven aircraft" \\ 
 10$:$30--11$:$00 & Omid Bidar, University of Sheffield. ``Data-driven turbulence model augmentation using DAFoam$:$ sparse sensor placement, and aerodynamic shape optimisation" \\  
  11$:$00--11$:$30 & Uttam Padmanaban, University of Southampton. ``Data assimilation of stalled airfoils using experimental reference data" \\  
  11$:$30--12$:$30 & How to promote a more interactive DAFoam community \\
  12$:$30--01$:$30 & Break
\end{tabularx}

\end{frame}
%---------------------------------------------------------------%

%---------------------------------------------------------------%
\begin{frame}{Schedule (Afternoon)}
\small
\begin{tabularx}{\textwidth}{lX}
 01$:$30--02$:$00 & Jeongbin Park, University of Michigan. ``Ducted hydrokinetic turbine design optimization using DAFoam" \\ 
 02$:$00--02$:$30 & Hossein Negahban, University of Quebec in Montreal. ``Aerodynamic shape optimization for morphing wing technology using DAFoam" \\ 
 02$:$30--03$:$00 & Karim Ahmed, Iowa State University. ``Field inversion of RANS modeling for transition flows" \\ 
 03$:$00--04$:$00 & Free discussion \\ 
\end{tabularx}

\end{frame}
%---------------------------------------------------------------%


\end{document}
